Single-Step Hybrid Prediction Report

### 2016-09-21 reports/agronomic_data.Rmd
Adjustments to kable() arguments

## Skewness
A general **rule of thumb** to consider is that skewed data whose ratio of the 
highest value to the lowest value is greater than 20 have significant skewness.
The formula for the skewness statistic is
$$
\text{skewness}  = \frac{\sum (x_i - \bar{x})^{3}}{(n - 1)v^{3/2}},
$$
where $v = \frac{\sum (x_i - \bar{x})^2}{(n - 1)}$ with $x$ is the predictor
variable, $n$ is the number of values and $\bar{x}$ is the sample mean of the 
predictor.
```{r Agro-Skewness, echo = FALSE}
all_skewness <- all_pheno %>%
  group_by(Trait) %>%
  summarize(Skewness = e1071::skewness(Observed),
            Skewness = round(Skewness, digits = 2))
reduced_skewness <- reduced_pheno %>%
  group_by(Trait) %>%
  summarize(Skewness = e1071::skewness(Observed),
            Skewness = round(Skewness, digits = 2))
full_join(x = all_skewness, y = reduced_skewness,
          by = "Trait",
          suffix = c(" (Full)", " (Reduced)")) %>%
  kable(padding = 0)
```

>>>>

## Skewness
A general rule of thumb to consider is that skewed data whose ratio of the 
highest value to the lowest value is greater than 20 have significant skewness.
The formula for the skewness statistic is
$$
\text{skewness}  = \frac{\sum (x_i - \bar{x})^{3}}{(n - 1)v^{3/2}},
$$
where $v = \frac{\sum (x_i - \bar{x})^2}{(n - 1)}$ with $x$ is the predictor
variable, $n$ is the number of values and $\bar{x}$ is the sample mean of the 
predictor.
```{r Agro-Skewness, echo = FALSE}
skew_tab_cap <- paste(
  "Skewness of seven agronomic traits for the full set of hybrids and the",
  "reduced set of hybrids, respectively."
)
all_skewness <- all_pheno %>%
  group_by(Trait) %>%
  summarize(Skewness = e1071::skewness(Observed),
            Skewness = round(Skewness, digits = 2))
reduced_skewness <- reduced_pheno %>%
  group_by(Trait) %>%
  summarize(Skewness = e1071::skewness(Observed),
            Skewness = round(Skewness, digits = 2))
full_join(x = all_skewness, y = reduced_skewness,
          by = "Trait",
          suffix = c(" (Full)", " (Reduced)")) %>%
  kable(caption = skew_tab_cap, booktable = TRUE)
```

### 2016-09-21 reports/index.Rmd
Adjustments to kable() arguments

---
title: Single-step Hybrid Predition
author: Matthias Westhues, Claas Heuer
date: "`r Sys.Date()`"
knit: "bookdown::render_book"
output:
  bookdown::gitbook:
documentclass: book
bibliography: ["cheuer.bib"]
biblio-style: apalike
link-citations: yes
---

>>>>

---
title: Single-step Hybrid Predition
author: Matthias Westhues, Claas Heuer
date: "`r Sys.Date()`"
knit: "bookdown::render_book"
output:
  bookdown::html_document2:
documentclass: book
bibliography: ["library.bib", "cheuer.bib"]
biblio-style: apalike
link-citations: yes
---

### 2016-09-21 reports/na_fraction_pheno_predability.Rmd
Adjustments to kable() arguments

# Prediction with Imputed mRNAs
```{r message = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load("data.table", "ggplot2", "ggthemes", "dplyr", "forcats", 
               "viridis", "tidyr")
knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", digits = 2)
})
knitr::opts_knit$set(root.dir = "~/gamazon/",
                     inline = TRUE)
knitr::opts_chunk$set(fig.width = 8, fig.height = 6,
                      warning = FALSE, echo = FALSE)
```

>>>>

# Prediction with Imputed mRNAs
```{r message = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load("data.table", "ggplot2", "ggthemes", "dplyr", "forcats", 
               "viridis", "tidyr")
knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", digits = 2)
})
knitr::opts_knit$set(root.dir = "~/gamazon/",
                     inline = TRUE)
knitr::opts_chunk$set(fig.width = 8, fig.height = 6,
                      warning = FALSE, echo = FALSE, message = FALSE)
```

### 2016-09-21 reports/single_step_pred.Rmd
Adjustments to kable() arguments

Consider now the situation in which only a subset of the population has 
transcriptomic information but all have SNP genotypes.
We can take a similar route as in @fernando_class_2014 and impute missing
mRNA data.
The difference here is that &mdash; instead of predicting SNP covariates using 
pedigree relationship &mdash; we impute MRNA covariates using SNP or genomic 
relationships.
Let the subscript $1$ denote individuals for which SNP genotypes but no mRNA 
data are available.
Individuals with subscript $2$ have both, SNP and mRNA information.
The covariates in $\mathbf{W}$ are centered.
The vector $\mathbf{g}_1$ can be written as the sum of the conditional 
expectation given $\mathbf{g}_2$ and a residual error term:
$$
\begin{align}
	\label{eq:mrna1}
	\mathbf{g_1} &= E(\mathbf{g}_1|\mathbf{g}_2) + \boldsymbol{\epsilon} \\
	&= \mathbf{G_{12}}\mathbf{G_{22}}^{-1}\mathbf{W_2}\boldsymbol{\hat{\alpha}} + (\mathbf{g_1} - \mathbf{G_{12}}\mathbf{G_{22}}^{-1}\mathbf{W_2}\boldsymbol{\hat{\alpha}}) \\
	&= \mathbf{\hat{g}}_1 + \boldsymbol{\epsilon}
\end{align}
$$

The distribution of $\boldsymbol{\epsilon}$ is $\mathbf{G}_{11} - \mathbf{G}_{12}\mathbf{G}_{22}^{-1}\mathbf{G}_{21} = (\mathbf{G}^{11})^{-1}$.

Using those results from @legarra_relationship_2009 we can model the breeding 
values of the individuals for wich no mRNA information is available the 
expectation of the breeding values in group $2$.
The structure of the residual imputation/prediction error is known and can 
therefore be modelled.
The missing mRNA covariates can be predicted using the expectation of a 
multivariate normal random vector given correlated observations, which related 
to the Best Linear Predictor.

>>>>

Consider now the situation in which only a subset of the population has 
transcriptomic information but all have SNP genotypes.
We can take a similar route as in @fernando_class_2014 and impute missing
mRNA data.
The difference here is that &mdash; instead of predicting SNP covariates using 
pedigree relationship &mdash; we impute MRNA covariates using SNP or genomic 
relationships.
Let the subscript $1$ denote individuals for which SNP genotypes but no mRNA 
data are available.
